---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# minty

<!-- badges: start -->
<!-- badges: end -->

`minty` (**Min**imal **TY**pe Inferencing and Parsing Tools) is an experimental package to spin off the type inferencing and parsing tools (the so-called 1e parsing engine) from `readr` (see this issue [tidyverse/readr#1517](https://github.com/tidyverse/readr/issues/1517)). Since July 2021, these tools are not used internally by `readr` for parsing text files. Now `vroom` is used by default, unless explicitly call the first edition parsing engine (see the explanation on [editions](https://github.com/tidyverse/readr?tab=readme-ov-file#editions)).

`readr`'s 1e type inferencing and parsing tools are used by various R packages, e.g. `readODS` and `surveytoolbox`, but ironically those packages do not use the main functions (e.g. `readr::read_delim()`) of `readr`. As explained in the README of `readr`, those 1e code will be eventually removed from `readr`.

`minty` aims at providing a set of minimal, long-term, and compatible type inferencing and parsing tools for those packages.

## Installation

You can install the development version of minty like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

A character-only data.frame

```{r}
text_only <- data.frame(maybe_age = c("17", "18", "20"),
                        maybe_male = c("true", "false", "true"),
                        maybe_name = c("AA", "BB", "CC"),
                        some_na = c("NA", "Not good", "Bad"),
                        dob = c("2019/07/21", "2019/08/31", "2019/10/01"))
str(text_only)
```

Inferencing the column types

```{r}
library(minty)
data <- type_convert(text_only)
data
```

```{r}
str(data)
```
