---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# minty

<!-- badges: start -->
[![R-CMD-check](https://github.com/chainsawriot/minty/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/chainsawriot/minty/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

`minty` (**Min**imal **TY**pe Inferencing and Parsing Tools) is an experimental package to spin off the type inferencing and parsing tools (the so-called 1e parsing engine) from `readr` (see this issue [tidyverse/readr#1517](https://github.com/tidyverse/readr/issues/1517)). Since July 2021, these tools are not used internally by `readr` for parsing text files. Now `vroom` is used by default, unless explicitly call the first edition parsing engine (see the explanation on [editions](https://github.com/tidyverse/readr?tab=readme-ov-file#editions)).

`readr`'s 1e type inferencing and parsing tools are used by various R packages, e.g. `readODS` and `surveytoolbox`, but ironically those packages do not use the main functions (e.g. `readr::read_delim()`) of `readr`. As explained in the README of `readr`, those 1e code will be eventually removed from `readr`.

`minty` aims at providing a set of minimal, long-term, and compatible type inferencing and parsing tools for those packages.

## Installation

You can install the development version of minty like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

A character-only data.frame

```{r}
text_only <- data.frame(maybe_age = c("17", "18", "019"),
                        maybe_male = c("true", "false", "true"),
                        maybe_name = c("AA", "BB", "CC"),
                        some_na = c("NA", "Not good", "Bad"),
                        dob = c("2019/07/21", "2019/08/31", "2019/10/01"))
str(text_only)
```

```{r}
## built-in function type.convert:
## except numeric, no type inferencing
str(type.convert(text_only, as.is = TRUE))
```

Inferencing the column types

```{r}
library(minty, warn.conflicts = FALSE)
data <- type_convert(text_only)
data
```

```{r}
str(data)
```

### Type-based parsing tools

```{r}
parse_datetime("1979-10-14T10:11:12.12345")
```

```{r}
fr <- locale("fr")
parse_date("1 janv. 2010", "%d %b %Y", locale = fr)
```

```{r}
de <- locale("de", decimal_mark = ",")
parse_number("1.697,31", local = de)
```

```{r}
parse_number("$1,123,456.00")
```

```{r}
## This is perhaps Python
parse_logical(c("True", "False"))
```

### Type guesser

```{r}
parse_guess(c("True", "TRUE", "false", "F"))
```

```{r}
parse_guess(c("123.45", "1990", "7619.0"))
```

```{r}
res <- parse_guess(c("2019-07-21", "2019-08-31", "2019-10-01", "IDK"), na = "IDK")
res
```

```{r}
str(res)
```
